---
title: "Reporting using quarto"
subtitle: "Reproducibility has never been easier"
institute: "ARCA initiative: Unlocking Psychological Expertise for Academic and Business Success"
author: "Ottavia M. Epifania"
format: 
  html:
    theme: 
     light: minty
     dark: darkly
    self-contained: true
    toc: true
    toc-location: left
execute: 
  echo: false
---

# The course

Reproducible reports integrate the code used for data analysis with the document that presents the findings, this enabling a continous flow between the analytical process and its interpretation.

While `R`Markdown undoubtely opened the way to this process, `quarto` represents the next generation, as it is even easier to use than `R`Markdown and includes new features, making the reporting process more accessible. 

This course provides an introduction to `quarto` and its basic features, along with a presentation on how to exploit it functionalities to create polished, professional outputs with embedded code chunks.

Some of the topics covered within this seminar are:

- Executable code chunks 
- Tables, charts, and references seamlessly.
- Reports and papers
- Presentations & so much more


## Course materials

All course materials are freely available on this website: 

- [00-Hello](slides/00-Hello/00-Hello.html) Let's get all set

- [01-Baby steps](slides/01-Baby-steps/01-Baby-steps.html) Formatting with markdwon, integration with github pages & layout

- [02-Code chunks](slides/02-Code-chunk/02-Code-chunk.html) How to control the executable code

- [03-Presentations](slides/03-Presentation/03-Presentation.html)

- [04-PDF Presentation](slides/04-PDF/04-PDF.pdf) with LaTeX

Here you can download the [dataset](data/dataset.csv) that we are going to use throughout the course 

# School Information

## Locations

Lectures will be at the Department of Statistical Sciences in via Cesare Battisti 241 Padova, ([https://maps.app.goo.gl/JMCthS2eZqWJEnmx8](https://maps.app.goo.gl/JMCthS2eZqWJEnmx8)), in **room SC20**.

```{r}
#| column: screen
library(leaflet)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  setView(lng = 11.885365425918087, lat = 45.40464995544754, zoom = 13) %>%
  addMarkers(lng = 11.885365425918087, lat = 45.40464995544754, popup = "Department of Statistics")
```

Lunch will be served at the University Mensa RistorEsu Nord Piovego in Viale Giuseppe Colombo 1, Padova [https://maps.app.goo.gl/Y8ta2wHzbsdn2cMF8](https://maps.app.goo.gl/Y8ta2wHzbsdn2cMF8)

```{r}
#| column: screen
library(leaflet)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  setView(lng =  11.890467829858775, 
          lat = 45.41117121174326, zoom = 13) %>%
  addMarkers(lng =  11.890467829858775, 
             lat = 45.41117121174326, popup = "RistorEsu Nord Piovego")

```

## Time schedule 


**THERE HAS BEEN A CHANGE IN THE PROGRAM ON FRIDAY, 25^TH^**

On Friday 25^th^, the quarto lesson will be in the morning session, while the R lesson will be in the afternoon session

### MONDAY, JULY 21

9:00 am - 9:30 am: check in
9:30 am - 12:30 pm: Dr. Angela Andreella

*Lunch break* 12:30 pm - 2:30 pm at RistorEsu Nord Piovego


2:30 pm - 5:30 pm: Dr. Marina Ottavia Epifania

### TUESDAY, JULY 22


9:00 am - 12:30 pm: Dr. Angela Andreella

*Lunch break 12:30 pm - 2:00 pm at RistorEsu Nord Piovego*

2:00 pm - 5:00 pm: Dr. Marina Ottavia Epifania

**6:00 pm - 7:00 pm: Guided tour at Orto Botanico**

### WEDNESDAY, JULY 23

9:00 am - 12:30 pm: Dr. Angela Andreella

*Lunch break 12:30 pm - 2:00 pm at RistorEsu Nord Piovego*

2:00 pm - 5:30 pm: Dr. Marina Ottavia Epifania

**Social Dinner 8:00 pm at Ristorante “Agli Eremitani”**

### THURSDAY, JULY 24

9:00 am - 12:30 pm: Dr. Angela Andreella
*Lunch break
12:30 pm - 2:00 pm at RistorEsu Nord Piovego*

2:00 pm - 5:30 pm: Dr. Marina Ottavia Epifania

### FRIDAY, JULY 25 Changed schedule

9:00 am - 12:00 pm:  Dr. Marina Ottavia Epifania 

*Lunch break 12:00 pm -1:30 pm at RistorEsu Nord Piovego*

1:30 pm - 5:00 pm: Dr. Angela Andreella


## Further activities

Visit to the [Botanical Garden](https://maps.app.goo.gl/X7nWgS3yWuARsKfo9) on Tuesday night, 6:00pm-7:00pm

Social dinner on Wednesday night at [Ristorante Agli Eremitani](https://maps.app.goo.gl/NzPXL1UWybYPZRre6), 8:00pm
